---
title: "Tables"
---

| Year	| Metric Tons	| Pounds	| Dive | Other |
|:---:|---:|---:|---:|---:|
| 2012	| 18.99	 | 41,869	 | 	97%	 |	3%	 |
| 2013	| 15.32	 | 33,773	 | 	98%	 |	2%	 |
| 2014	| 9.88	 | 21,774	 | 	87%	 |	13%	 |
| 2015	| 11.25	 | 24,808	 | 	68%	 |	32%	 |
| 2016	| 11.10	 | 24,481	 | 	58%	 |	42%	 |
| 2017	| 10.67	 | 23,533	 | 	68%	 |	32%	 |
| 2018	| 3.29	 | 7,262	 | 	90%	 |	10%	 |
| 2019	| 3.42	 | 7,540	 | 	80%	 |	20%	 |
| 2020	| 9.93	 | 21,883	 | 	71%	 |	29%	 |
| 2021	| 11.07	 | 24,412	 | 	90%	 |	10%	 |
| 2022	| 7.44	 | 16,398	 | 	74%	 |	26%	 |
| Total	| 112.37 | 247,733 | 	82%	 |	18%	 |

:  Commercial landings of Stoplight Parrotfish reported in St. Croix from
2012-2022 in metric tons and pounds by year, along with the percentage of the total commercial landings that came from each gear group.  {#tbl-catch}

{{< pagebreak >}}

| Input Source | Input Type | Input | M | Method |
|:-----------|:-----------|:--------:|:--:|:--------|
| @choat2003 | Maximum age | 30 | 0.180 | Hamel_Amax |
| **SEDAR84-AP-01** | **Maximum age** | **20** | **0.270** | **Hamel_Amax** |
| Meta-analysis | Scientific name | *Sparisoma viride* | 0.397 | FishLife |
| @choat2003 | Maximum age | 12 | 0.450 | Hamel_Amax |
| @choat2003 | Maximum age | 9 | 0.600 | Hamel_Amax |
| SEDAR84-AP-01 | Growth (k) | 0.39 | 0.604 | Hamel_k |
| SEDAR84-AP-01 | Growth (k) | 0.39 | 0.585 | Jensen_k 1 |
| SEDAR84-AP-01 | Growth (k) | 0.39 | 0.624 | Jensen_k 2 |
| SEDAR84-AP-01 | Growth (L∞, k) | 33.2, 0.39 | 0.576 | Then_VBGF |
| SEDAR84-AP-01 | Growth (k) | 0.33 | 0.512 | Hamel_k |
| SEDAR84-AP-01 | Growth (k) | 0.33 | 0.495 | Jensen_k 1 |
| SEDAR84-AP-01 | Growth (k) | 0.33 | 0.528 | Jensen_k 2 |
| SEDAR84-AP-01 | Growth (L∞, k) | 33.8, 0.33 | 0.573 | Then_VBGF |
| SEDAR84-AP-01 | Age at 50% maturity | 1.6 | 1.030 | Jensen_Amat |
| SEDAR84-AP-01 | Age at 50% maturity | 1.6 | 0.924 | Ri_Ef_Amat |

: Empirical estimates of natural mortality (M) can be derived using life history information and the Natural Mortality Tool [@cope2022]. The SEDAR assessment working paper SEDAR84-AP-01 is equivalent to @riverahernández2024.  {#tbl-m}

{{< pagebreak >}}

| Model Development Process | Code | Sequential modeling steps |
|---------------------------|:----:|-----------------------------|
| Data-limited | null | super-year size data |
| **Data-moderate** | **a** | **index** |
| **Data-moderate** | **b** | **annual fishery-independent size data** |
| Data-moderate | c | annual fishery-dependent size data |
| Data-moderate | d | recruitment deviations |
| Data-moderate | e | dome-shaped selectivity |
| Data-moderate | f | time blocks |
| **Variation 1** | **v1** | **a + b** |
| Variation 2| v2 | a + c |
| **Variation** 3| **v3** | **a + d** |
| Variation 4 | v4 | a + e |
| Variation 5 | v5 | a + f |
| Variation 6 | v6 | a + b + c |
| **Variation** 7| **v7** | **a + b + d** |
| Variation 8 | v8 | a + b + e |
| Variation 9 | v9 | a + b + f |
| Variation 10 | v10 | a + c + d |
| Variation 11 | v11 | a + c + e |
| Variation 12 | v12 | a + c + f |
| Variation 13 | v13 | a + d + e |
| Variation 14 | v14 | a + d + f |
| Variation 15 | v15 | a + e + f |
| Variation 16 | v16 | a + b + c + d |
| Variation 17 | v17 | a + b + c + e |
| Variation 18 | v18 | a + b + c + f |
| Variation 19 | v19 | a + b + d + e |
| Variation 20 | v20 | a + b + d + f |
| Variation 21 | v21 | a + b + e + f |
| Variation 22 | v22 | a + b + c + d + e |
| Variation 23 | v23 | a + b + c + d + f |
| Variation 24 | v24 | a + b + c + e + f |
| Variation 25 | v25 | a + b + c + d + e + f |

:  Summary of process and naming conventions used for SEDAR 84 assessments describing  model development noting the simplest data-limited configuration, exploring individual data-moderate considerations, individually and combined.  {#tbl-overview}

| Stage | Code | Sequential modeling steps |
|--------|:----:|----------------------------------------------------------------|
| Initial	| ct	| model initialized with continuum tool (ct) |
| Initial	| m1	| ct + hermaphroditism |
| Initial	| m2	| m1 + continuous recruitment |
| Initial | m3  | m2 + catch uncertainty |
| Scenario  | null | super-year size data |
| Scenario	| a	| index |
| Scenario	| b	| annual fishery-independent size data |
| Scenario	| v1	| index + annual fishery-independent size data |
| Scenario	| v3	| index + recruitment deviations |
| Scenario	| v7	| index + annual fishery-independent size data + recruitment deviations |
| Sensitivity	| s1	| higher CV on growth young |
| Sensitivity	| s2	| higher age and lower m |
| Sensitivity	| s3	| one sex (age-based fecundity = maturity * weight * sex ratio)  |
| **Sensitivity**	| **s4**	| **higher catch uncertainty** |
| Sensitivity	| s5	| s2 + s4 |
| Sensitivity	| s6	| s2 + s3 + s4 |

:  Summary of process and naming conventions used across different model development stages of the SEDAR 84 St. Croix Stoplight Parrotfish stock assessment.  {#tbl-ss3-stxslp}

{{< pagebreak >}}

```{r}
#| echo: false
#| warning: false
#| label: tbl-corr
#| tbl-cap: "St. Croix stoplight parrotfish correlations between estimated parameters by modeling scenario. The table shows correlations greater than 0.9 or less than -0.9. Correlations that are greater than 0.95 or less than -0.95 are shown in red."

library(here)
library(dplyr)
library(flextable)

short_covar <- read.csv(here::here("Scenarios", "scenarios_covar.csv")) |>
  dplyr::mutate(
    label.i = dplyr::case_when(
      label.i == "InitF_seas_1_flt_1Commercial" ~ "Initial F",
      label.i == "Size_DblN_ascend_se_Commercial(1)" ~ "Commercial Selectivity Asend."
    ),
    label.j = dplyr::case_when(
      label.j == "SR_LN(R0)" ~ "Unfished Recruitment (R0)",
      label.j == "Size_DblN_peak_Commercial(1)" ~ "Commercial Selectivity Peak"
    )
  )

var_corr <- c(
  "Scenario",
  "Estimated Parameters", 
  "Estimated Parameters", 
  "Correlation")

tbl_corr <- short_covar |>
  dplyr::filter(stringr::str_detect(scenario, "m2$|m3$" )) |>
  flextable::flextable() |>
  flextable::autofit() |>
  flextable::align(align = "center", part = "all") |>
  flextable::set_header_labels(values = var_corr) |>
  flextable::merge_h(part = "header") |>
  flextable::color(color = "red", j = "corr", i = ~ abs(corr) > 0.95) |>
  flextable::fontsize(size = 11, part = "all") |>
  flextable::font(fontname = "Times New Roman", part = "all")

tbl_corr

```

{{< pagebreak >}}

```{r}
#| label: tbl-eqcatch
#| tbl-cap: "St. Croix stoplight parrotfish estimated initial equilibrium catch in metric tons by model scenario. The input value was 30 metric tons with a standard error of 0.3."

est_eqcatch_short <- read.csv(here::here("Scenarios", "eq_catch.csv")) |>
  dplyr::mutate(Estimate = round(Estimate, 2)) |>
  dplyr::filter(!stringr::str_detect(Scenario, "ct|m1" )) |>
  tidyr::separate(Scenario, c('run', 'Scenario'), sep = "_", extra = "merge") |>
  tidyr::pivot_wider(
    names_from = c(run),
    values_from = c(Estimate))

tbl_eqcatch <- est_eqcatch_short |>
  flextable::flextable() |>
  flextable::autofit() |>
  flextable::theme_box() |>
  flextable::align(align = "center", part = "all") |>
  flextable::merge_v(j = "Parameter") |>
  flextable::fontsize(size = 11, part = "all") |>
  flextable::font(fontname = "Times New Roman", part = "all")

tbl_eqcatch

```

{{< pagebreak >}}

```{r}
#| label: tbl-parm
#| tbl-cap: "St. Croix stoplight parrotfish parameters, standard deviations (SD), and coefficient of variation (CV) by modeling scenario. CV is calculated as the SD divided by the parameter estimate."

est_parm_short <- read.csv(here::here("Scenarios", "scenarios_parm.csv")) |>
  dplyr::mutate(
    Parameter = dplyr::case_when(
      Parameter == "InitF_seas_1_flt_1Commercial" ~ "Initial F",
      Parameter == "Size_DblN_ascend_se_Commercial(1)" ~ "Commercial Selectivity Asend.",
      Parameter == "SR_LN(R0)" ~ "Unfished Recruitment (R0)",
      Parameter == "Size_DblN_peak_Commercial(1)" ~ "Commercial Selectivity Peak"
    )
  ) |>
  dplyr::select(Parameter, Scenario, Estimate, SD, CV) |>
  dplyr::arrange(Parameter, Scenario) |>
  dplyr::filter(stringr::str_detect(Scenario, "\\w*m3$"))


tbl_parm <- est_parm_short |>
  flextable::flextable() |>
  flextable::autofit() |>
  flextable::theme_box() |>
  flextable::align(align = "center", part = "all") |>
  flextable::merge_v(j = "Parameter") |>
  flextable::fontsize(size = 11, part = "all") |>
  flextable::font(fontname = "Times New Roman", part = "all")

tbl_parm

```

```{r}
#| label: tbl-dq
#| tbl-cap: "St. Croix stoplight parrotfish derived quantities for unfished and initial spawning stock biomass in metric tons (mt) along with standard deviations (SD) and coefficient of variation (CV) by modeling scenario. CV is calculated as the SD divided by the parameter estimate."

est_dq <- read.csv(here::here("Scenarios", "scenarios_dq.csv")) |>
  dplyr::mutate(
    Parameter = dplyr::case_when(
      Parameter == "SSB_Initial" ~ "SSB Initial (mt)",
      Parameter == "Bratio_2012" ~ "Ratio SSB \nInitial:Unfished",
      Parameter == "SSB_unfished" ~ "SSB Unfished (mt)"
    )
  ) |>
  dplyr::select(Parameter, Scenario, Estimate, SD, CV) |>
  dplyr::arrange(desc(Parameter), Scenario) |>
  dplyr::filter(stringr::str_detect(Scenario, "\\w*m3$"))


tbl_dq <- est_dq |>
  dplyr::rename("Derived Quantity" = Parameter) |>
  flextable::flextable() |>
  flextable::autofit() |>
  flextable::theme_box() |>
  flextable::align(align = "center", part = "all") |>
  flextable::merge_v(j = "Derived Quantity") |>
  flextable::fontsize(size = 11, part = "all") |>
  flextable::font(fontname = "Times New Roman", part = "all")

tbl_dq

```

{{< pagebreak >}}

```{r}
#| label: tbl-est-msy
#| tbl-cap: "St. Croix stoplight parrotfish derived quantities for MSY SPR 40%. CV is calculated as the SD divided by the parameter estimate."

est_msy <- read.csv(here::here("Scenarios", "est_msy.csv")) |>
  dplyr::filter(!stringr::str_detect(Scenario, "ct|m1" ))


tbl_est_msy <- est_msy |>
  flextable::flextable() |>
  flextable::autofit() |>
  flextable::theme_box() |>
  flextable::align(align = "center", part = "all") |>
  flextable::fontsize(size = 11, part = "all") |>
  flextable::font(fontname = "Times New Roman", part = "all")

tbl_est_msy

```

{{< pagebreak >}}

```{r}
#| label: tbl-msy
#| tbl-cap: "St. Croix stoplight parrotfish estimated MSY SPR 40% in pounds."

scenarios_summary <- read.csv(here::here("Scenarios", "scenarios_summary.csv")) |>
  dplyr::select(scenario, Dead_Catch_SPR_lbs) |>
  dplyr::filter(!stringr::str_detect(scenario, "ct|m1" )) |>
  tidyr::separate(scenario, c('run', 'Scenario'), sep = "_", extra = "merge") |>
  tidyr::pivot_wider(
    names_from = c(run),
    values_from = c(Dead_Catch_SPR_lbs))

tbl_msy <- scenarios_summary |>
  flextable::flextable() |>
  flextable::autofit() |>
  flextable::theme_box() |>
  flextable::align(align = "center", part = "all") |>
  flextable::fontsize(size = 11, part = "all") |>
  flextable::font(fontname = "Times New Roman", part = "all")

tbl_msy

```
```{r}
#| label: tbl-spr-f
#| tbl-cap: "St. Croix stoplight parrotfish estimated MSY SPR 40% in pounds."

spr_f_summary <- read.csv(here::here("Scenarios", "scenarios_summary.csv")) |>
  dplyr::select(scenario, Fcurrent_FSPR) |>
  dplyr::mutate(Fcurrent_FSPR = round(Fcurrent_FSPR, 2)) |>
  dplyr::filter(!stringr::str_detect(scenario, "ct|m1" )) |>
  tidyr::separate(scenario, c('run', 'Scenario'), sep = "_", extra = "merge") |>
  tidyr::pivot_wider(
    names_from = c(run),
    values_from = c(Fcurrent_FSPR)) |>
  dplyr::mutate(Metric = "F Current / F SPR 40%")

spr_ssb_summary <- read.csv(here::here("Scenarios", "scenarios_summary.csv")) |>
  dplyr::select(scenario, SSB2022_SSBSPR) |>
  dplyr::mutate(SSB2022_SSBSPR = round(SSB2022_SSBSPR, 2)) |>
  dplyr::filter(!stringr::str_detect(scenario, "ct|m1" )) |>
  tidyr::separate(scenario, c('run', 'Scenario'), sep = "_", extra = "merge") |>
  tidyr::pivot_wider(
    names_from = c(run),
    values_from = c(SSB2022_SSBSPR)) |>
  dplyr::mutate(Metric = "SSB 2022 / SSB SPR 40%")

msra_summary = rbind(spr_f_summary, spr_ssb_summary) |>
  dplyr::relocate(Metric) 
  

tbl_msra <- msra_summary |>
  flextable::flextable() |>
  flextable::autofit() |>
  flextable::theme_box() |>
  flextable::merge_v(j = "Metric") |>
  flextable::align(align = "center", part = "all") |>
  flextable::fontsize(size = 11, part = "all") |>
  flextable::color(color = "red", i = ~ a > 1 & Metric == "F Current / F SPR 40%", j = "a") |>
  flextable::color(color = "red", i = ~ b > 1 & Metric == "F Current / F SPR 40%", j = "b") |>
  flextable::color(color = "red", i = ~ v1 > 1 & Metric == "F Current / F SPR 40%", j = "v1") |>
  flextable::color(color = "red", i = ~ v3 > 1 & Metric == "F Current / F SPR 40%", j = "v3") |>
  flextable::color(color = "red", i = ~ v7 > 1 & Metric == "F Current / F SPR 40%", j = "v7") |>
    flextable::align(align = "center", part = "all") |>
  flextable::fontsize(size = 11, part = "all") |>
  flextable::color(color = "red", i = ~ a < 1 & Metric == "SSB 2022 / SSB SPR 40%", j = "a") |>
  flextable::color(color = "red", i = ~ b < 1 & Metric == "SSB 2022 / SSB SPR 40%", j = "b") |>
  flextable::color(color = "red", i = ~ v1 < 1 & Metric == "SSB 2022 / SSB SPR 40%", j = "v1") |>
  flextable::color(color = "red", i = ~ v3 < 1 & Metric == "SSB 2022 / SSB SPR 40%", j = "v3") |>
  flextable::color(color = "red", i = ~ v7 < 1 & Metric == "SSB 2022 / SSB SPR 40%", j = "v7") |>
  flextable::font(fontname = "Times New Roman", part = "all")

tbl_msra

```